---
header-includes:
   \usepackage{amsmath}
   \usepackage{geometry}
   \usepackage{pdfpages}
   \usepackage{fontspec}
   \usepackage{pdfpages}
   \usepackage{graphicx}
   \usepackage{amsmath}
   \usepackage{atbegshi}
   \usepackage{fancyhdr}
   \usepackage{tocloft}
   \usepackage{tcolorbox}
   \usepackage{xcolor}
   \definecolor{bleu}{RGB}{0,0,255}
   \usepackage{everypage}
   \usepackage{everypage}
   \usepackage{graphicx}
   \usepackage{fancyhdr}
   \pagestyle{fancy} 
   \definecolor{mybrown}{RGB}{139,69,19}
   \fancyhead[R]{}
output: 
  pdf_document: 
    number_sections: true
    latex_engine: xelatex
    fig_height: 4
    fig_width: 5
    fig_caption: true
    keep_tex: true
lang: fr
bibliography: references.bib
urlcolor: blue
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

\setcounter{tocdepth}{5}                
\renewcommand\contentsname{\begin{center}\textcolor{brown}{Sommaire}\end{center}}
\AtBeginShipout{
  \ifnum\value{page}=1\thispagestyle{empty}\fi}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\fancyhead[L]{Elèves Ingénieurs}
\fancyhead[R]{\textcolor{brown}{@Alex, Ali, Richard \& Toussaint}}
\fancyfoot[C]{\thepage}
\fancyfoot[L]{Mars 2025}
\fancyfoot[R]{Projet Statistique}
\AddEverypageHook{
  \ifnum\value{page}>1 
    \fancyhead[L]{Elèves Ingénieurs}
    \fancyhead[R]{\textcolor{brown}{@Alex, Ali, Richard \& Toussaint}}
    \fancyfoot[C]{\thepage}
    \fancyfoot[L]{Mars 2025}
    \fancyfoot[R]{Projet Statistique}
  \else
    \fancyhead[L]{} 
    \fancyhead[R]{}
    \fancyfoot[C]{}
    \fancyfoot[R]{}
  \fi
}
```{=latex}
\tableofcontents
```

\newpage

\renewcommand\listtablename{\begin{center}\textcolor{brown}{Liste des Tableaux}\end{center}}
\renewcommand\listfigurename{\begin{center}\textcolor{brown}{Liste des Figures}\end{center}} 

\setlength{\cftfignumwidth}{3em}
\setlength{\cfttabnumwidth}{3em}
```{=latex}
\listoftables
```

\newpage

```{=latex}
\listoffigures
```

\newpage

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```


```{r child="1_Introduction.Rmd"}
```


```{r child= "2_Contexte_Revue.Rmd"}

```


```{r child= "3_Methodologie.Rmd"}

```

```{r child= "4_Analyse_Descriptive.Rmd"}

```


```{r child= "8_Annexes.Rmd"}

```

